---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 5 & 6"
author: "Alex Schweizer"
output: html_notebook
---

## Assigned Exercises
* DC Chapter 5 Exercises: 5.1, 5.2
* DC Chapter 6 Exercises: 6.5, 6.6, 6.7, 6.8

## Front Matter 
```{r}
# Cleaning up environment
rm(list=ls())
# All Packages Needed in Assignment
library(mosaicData)
library(DataComputing)
library(mosaic)
```

## Chapter 5 Exercises 

### Problem 5.1
"Use barGraphHelper() to reconstruct the graph. Start with these commands:" 

```{r}
barGraphHelper(CPS85)
```
"Don't know how to show you that I used the gear icon to manipulate the data into the correct form" 

### Problem 5.2
"Make this graph from the NCHS data in the DataComputing package." 

```{r}
densityGraphHelper(NCHS,format="frequency polygon")
```
"Don't know how to show you that I used the gear icon to manipulate the data into the correct form" 

## Chapter 6 Exercises 

### Problem 6.5 

"In the figure, what variables define the frame?"

* B.) State and Polling Organization 

### Problem 6.6 

"In the figure, what is the glyph and its graphical attributes?"

* D.) Glyph: Rectangle. Graphical attribute: color and text.

### Problem 6.7 

"In the figure, what sets the order of the categorical variable in the scale for the vertical variable?" 

* D.) NYT poll probability for the Democratic candidate. 

### Problem 6.8 

"In the figure, which of these is a guide for the indicated graphical attribute? (Select all that apply.)" 

* A.) Vertical scale: Name of state.
* E.) Color: Color Band 

